|

### 2022-06-10 paper.Rmd
add missing nums

`r nrow(got_reviews_from)` of these tools had received user reviews (`r num_tools_w_reviews_by_store %>% filter(store == "chrome") %>% pull(n)` from Chrome Web, `r num_tools_w_reviews_by_store %>% filter(store == "google_play") %>% pull(n)` from Google Play, and `r num_tools_w_reviews_by_store %>% filter(store == "apple") %>% pull(n)` from the Apple App store). 
From these, we collected a total of `r format(nrow(reviews_w_main_cat_data), big.mark = ",")` reviews (`r num_reviews_by_store %>% filter(store == "chrome") %>% pull(n) %>% format(big.mark = ",")` from Chrome Web, `r num_reviews_by_store %>% filter(store == "google_play") %>% pull(n) %>% format(big.mark = ",")` from Google Play, and `r num_reviews_by_store %>% filter(store == "apple") %>% pull(n) %>% format(big.mark = ",")` from the Apple App store).

@@

The distribution of numbers of users/installations and ratings are shown in Figure \ref{fig:tool-num-users-and-ratings-plot}.
For Google Play tools, the median 'minimum number of installs' was `r format(play_user_stats$median_min_installs, big.mark = ",")` (min = `r format(play_user_stats$min_min_installs, big.mark = ",")`, max = `r format(play_user_stats$max_min_installs, big.mark = ",")`, IQR = `r format(play_user_stats$q25_min_installs, big.mark = ",")` to `r format(play_user_stats$q75_min_installs, big.mark = ",")`). 
For Chrome Web tools, the median number of users was `r format(chrome_user_stats$media_installs, big.mark=",")` (min = `r format(chrome_user_stats$min_installs, big.mark=",")`, max = `r format(chrome_user_stats$max_installs, big.mark=",")`, IQR = `r format(chrome_user_stats$q25_installs, big.mark=",")` to `r format(chrome_user_stats$q75_installs, big.mark=",")`). 
The Apple App store did not display information about number of users (the median number of ratings for DSCTs from the Apple App store was `r format(num_ratings_apple$median, big.mark=",")`; max = `r format(num_ratings_apple$max, big.mark=",")`, IQR = `r format(num_ratings_apple$q25, big.mark=",")` to `r format(num_ratings_apple$q75, big.mark=",")`). 
The median average rating across all tools was `r format(ratings_overall$median_rating, big.mark=",")` (min = `r format(ratings_overall$min_rating, big.mark=",")`, max = `r format(ratings_overall$max_rating, big.mark=",")`, IQR = `r format(ratings_overall$q25_rating, big.mark=",")` to `r format(ratings_overall$q75_rating, big.mark=",")`; ratings given on a scale from 1 to 5 stars on all stores).

>>>>

`r nrow(got_reviews_from)` of these tools had received user reviews (`r num_tools_w_reviews_by_store %>% filter(store == "chrome") %>% pull(n)` from Chrome Web, `r num_tools_w_reviews_by_store %>% filter(store == "play") %>% pull(n)` from Google Play, and `r num_tools_w_reviews_by_store %>% filter(store == "apple") %>% pull(n)` from the Apple App store). 
From these, we collected a total of `r format(nrow(reviews_w_main_cat_data), big.mark = ",")` reviews (`r num_reviews_by_store %>% filter(store == "chrome") %>% pull(n) %>% format(big.mark = ",")` from Chrome Web, `r num_reviews_by_store %>% filter(store == "play") %>% pull(n) %>% format(big.mark = ",")` from Google Play, and `r num_reviews_by_store %>% filter(store == "apple") %>% pull(n) %>% format(big.mark = ",")` from the Apple App store).

@@

The distribution of numbers of users/installations and ratings are shown in Figure \ref{fig:tool-num-users-and-ratings-plot}.
For Google Play tools, the median 'minimum number of installs' was `r format(play_user_stats$median_min_installs, big.mark = ",")` (min = `r format(play_user_stats$min_min_installs, big.mark = ",")`, max = `r format(play_user_stats$max_min_installs, big.mark = ",")`, IQR = `r format(play_user_stats$q25_min_installs, big.mark = ",")` to `r format(play_user_stats$q75_min_installs, big.mark = ",")`). 
For Chrome Web tools, the median number of users was `r format(chrome_user_stats$median_installs, big.mark=",")` (min = `r format(chrome_user_stats$min_installs, big.mark=",")`, max = `r format(chrome_user_stats$max_installs, big.mark=",")`, IQR = `r format(chrome_user_stats$q25_installs, big.mark=",")` to `r format(round(chrome_user_stats$q75_installs), big.mark=",")`). 
The Apple App store did not display information about number of users (the median number of ratings for DSCTs from the Apple App store was `r format(num_ratings_apple$median, big.mark=",")`; max = `r format(num_ratings_apple$max, big.mark=",")`, IQR = `r format(num_ratings_apple$q25, big.mark=",")` to `r format(num_ratings_apple$q75, big.mark=",")`). 
The median average rating across all tools was `r format(ratings_overall$median_rating, big.mark=",")` (min = `r format(ratings_overall$min_rating, big.mark=",")`, max = `r format(ratings_overall$max_rating, big.mark=",")`, IQR = `r format(round(ratings_overall$q25_rating), nsmall=1)` to `r format(round(ratings_overall$q75_rating), nsmall=1)`; ratings given on a scale from 1 to 5 stars on all stores).
